%%==================================%%
%%          生成本科生标题           %%
%%			    无需修改			%%
%%==================================%%
\makecntitle
%%==================================%%
%%             中文摘要             %%
%%==================================%%
\abstract
% \lipsum[xx] 和 \zhlipsum[xx][xx] 等命令为测试使用的随机文本命令
% 使用模板写作时请删除，下同
{
	高校科研经费规模的快速扩张，导致传统管理模式在应对多维财务数据时面临较大的处理压力，风险预警滞后与决策工具不足是目前管理实操中普遍存在的短板。针对这些技术痛点，本文基于 Spring Boot 与 Vue 3 架构开发了一套经费决策支持系统，通过六级状态机闭环逻辑，将审批、预算、审计及验收环节整合为端到端管理链条。安全层面，利用 BCrypt 强哈希算法加固认证标识。

    系统的核心在于多维数据决策引擎，它通过抓取进度完成情况、资金执行率等核心指标，并利用 ECharts 转化为直观的可视化看板。系统能主动捕捉“执行滞后”或“余额耗尽”等异常信号并输出针对性建议。根据系统上线后的运行数据，审计响应周期的压缩直接带动了科研经费管理效率的增长，且提升幅度远超预期。这种从开发构思到业务实操的快速转化，证明了该工具在解决落地周期冗长这一问题上的可行性。
}

%% ==== 关键词
\keywords{科研经费管理；多维数据分析；决策支持；Spring Boot；系统开发}

%%==================================%%
%%          生成本科生标题           %%
%%			    无需修改			%%
%%==================================%%
\makeentitle

%%==================================%%
%%             英文摘要             %%
%%==================================%%
%% 使用带选项\abstract[Abstract]命令添加英文摘要
\abstract[Abstract]
% ==== 随机文本，使用模板时请删除
{
	With the vigorous development of university scientific research, the number of research projects and the scale of funds have increased dramatically. Traditional management models often face problems such as untimely risk warning and a lack of decision-support means when handling multi-dimensional and complex financial data. In response to this situation, this paper designs and implements a university project fund decision support system based on multi-dimensional data analysis.

    The system is built on a front-end/back-end separation architecture based on Spring Boot and Vue 3, and uses MyBatis-Plus to improve data persistence efficiency. At the business logic layer, the system constructs a six-level state machine closed-loop process, covering project approval, budget preparation, expenditure auditing, and final acceptance, achieving end-to-end management of the project lifecycle. For example, from a security design perspective, the system introduces a strong hash algorithm (BCrypt) to encrypt and store user passwords, thereby protecting the security of system authentication identifiers. The core of this framework is a multi-dimensional data decision support engine. It extracts key indicators, such as progress completion, fund execution rate, and account balance percentage, and uses ECharts to provide visual dashboards. It can automatically identify potential risks such as "execution delays" and "balance depletion," and provide targeted decision support suggestions.
    
    The system's stability has been tested, and it runs stably after functional and performance testing. It can significantly improve the efficiency of research funding utilization, shorten the audit response cycle, and shorten the time from development to practical application of university research decision support tools.
}
% ==== 英文关键词
\keywords[Key words]{Research Fund Management; Multi-dimensional Data Analysis; Decision Support; Spring Boot; System Development}